Kids PM Summary

### 2020-05-21 exposure_models.Rmd
small exposure model/figure updates

>>>>

```{r}
# Look at R^2 for final selected model
model_results <- lm(log_pm_mean_sampling_period ~
                      income_3level +
                      residents_smoke +
                      home_year_built_2level +
                      home_floors_2level + 
                      home_pets_2level +
                      chimney_clean_3level +
                      home_fireplace +
                      wood_collect_2level +
                      sums_events_sampling_period +
                      mean_temp_sampling_period_5,
                      data = imputed_exposure_data$data)

summary(model_results)
```

### 2020-05-21 manuscript_tables_figures.Rmd
small exposure model/figure updates

```{r}
# number of placebo households, total and by area
placebo_homes <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>%
  count(area)
placebo_homes

# number of placebo households, total and by area
treatment_homes <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  count(treatment)
treatment_homes

# number of placebo households, total and by area
treatment_kids <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 2) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  filter(!is.na(child_id_num)) %>% 
  count(treatment)
treatment_kids
```

>>>>

```{r}
# number of placebo households, total and by area
placebo_homes <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>%
  count(area)
placebo_homes

# number of placebo households, total and by area
treatment_homes <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 2) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(area) %>% 
  count(treatment)
treatment_homes

# number of placebo households, total and by area
treatment_kids <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 2) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  filter(!is.na(child_id_num)) %>% 
  group_by(area) %>% 
  count(treatment)
treatment_kids
```

### 2020-05-21 pm_summary.Rmd
small exposure model/figure updates

```{r}
# Load data
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
pm_clean <- read_rds(paste0(output_path, "Output/pm_clean.rds"))
```

>>>>

```{r}
# Load data
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

pm_clean <- read_rds(paste0(file_path, "Output/pm_clean.rds"))

exposure_analysis_data_long <- 
  read_rds(paste0(file_path, "Output/exposure_analysis_data_long_new.rds"))

exposure_analysis_data_medium <- 
  read_rds(paste0(file_path, "Output/exposure_analysis_data_medium.rds"))

exposure_analysis_data_short <- 
  read_rds(paste0(file_path, "Output/exposure_analysis_data_short.rds"))

sums_rolling_pm_data <- 
  read_rds(paste0(file_path, "Output/sums_rolling_pm_data.rds"))
```

```{r}
# home that exceed PM guidelines
pm_guidelines <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(pm_mean_sampling_period > 35) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(area) %>% 
  count()
pm_guidelines
```
